---
title: "Simulations Pre-Class Project"
date: "Due March 13, 2017 at 5:00pm"
output:
  html_document


---

<style type="text/css">
.table {

    width: 80%;
    margin-left:10%; 
    margin-right:10%;
}
</style>
```{r,setup, echo=FALSE, cache=TRUE}
## numbers >= 10^5 will be denoted in scientific notation,
## and rounded to 2 digits
options(scipen = 3, digits = 3)
```




#Project Goals:


With this project we will simulate a famoues probability problem. This will not require knowledge of probability or statistics but only the logic to follow the steps in order to simulate this problem. This is one way to solve problems by using the computer. 

 1. **Gambler's Ruin**: Suppose you have a bankroll of $1000 and make bets of $100 on a fair game. By simulating the outcome directly for at most 5000 iterations of the game (or hands), estimate:
 
```{r}
#set.seed(1)
GR=function(bets,bankroll,prob){
  k=0
  while(bets>0) {       #while there are any bets
    pval=runif(1)       #the probability value runs a normal random number
    if(pval <= prob)    #if the probability value is less than or equal to the given 'prob' argument then run...
    {
      bankroll = bets + bankroll     
      bets = (bets + bankroll)*0.1
    }else{
      bankroll = bankroll-bets
      bets = bets
      }
    k=k+1
    if(bankroll < bets){break}
  }
  durations = k
  return(durations)
}

durations = numeric()
s = 5000
for(i in 1:s)
{
  nextd = GR(100,900,0.5)
  durations = c(durations,nextd)
}

```

a. the probability that you have "busted" (lost all your money) by the time you have placed your one hundredth bet.
```{r}
a1a=length(durations)
b1a=length(which(durations<=100))
prob1a=b1a/a1a
prob1a

```


