# pre-class


Make sure you commit this often with meaningful messages. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
#function name: prefix_test
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}

#function name: delete_last
f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}

#function name: total_rep
f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?

```{r}
##rnorm is a univariate version, while MASS::mvrnorm is multivariate. This means that although they both sample from normal distributions, they are different types of normal distributions, and therefore have different spreads and different arguments. 
##I think it would be a good idea to try and make MASS::mvrnorm more similar to rnorm, but due to the differences in arguments, spread, and distribution, it is difficult.
```


3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 

```{r}
lapply(mtcars, function(x) sd(x)/mean(x))
```

4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)
```{r}
#A


#B

```
